\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{helvet}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\familydefault}{\sfdefault}
\urlstyle{same}
\raggedbottom
\raggedright

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.08003pt}

% Personal Information
\newcommand{\name}{Darien Ford}
\newcommand{\email}{darien.ford99@gmail.com}
\newcommand{\website}{darien-ford.com}
\newcommand{\linkedin}{in/darienford}

% Personal Links
\newcommand{\emailLink}{mailto:darien.ford99@gmail.com}
\newcommand{\websiteLink}{https://www.darien-ford.com}
\newcommand{\linkedinLink}{https://www.linkedin.com/in/darienford}
\newcommand{\githubLink}{https://www.github.com/Darien-Ford}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1}\vspace{-2pt}
  }
}

\newcommand{\resumeSubHeading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {#2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeTitle}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      {\small#1} & {\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label=,leftmargin=]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeTitleStart}{\begin{itemize}[label=,leftmargin=]}
\newcommand{\resumeTitleEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=\textbullet]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% HEADER
\begin{center}
     \textbf{\huge{\name}}\bigskip\\
 
    \begin{tabular}{c c c c c}
    
        \href{\emailLink}{\faEnvelopeO\enspace{\email}} & \href{\websiteLink}{\faDesktop\enspace{\website}} & \href{\linkedinLink}{\faLinkedin\enspace{\linkedin}} & \href{\githubLink}{\faGithub\enspace{GitHub}}\\
        
    \end{tabular}
\end{center}

% EXPERIENCE
\section{Experience}
    \resumeSubHeadingListStart

    \resumeSubHeading{Kawasaki Robotics}{Wixom, Michigan}\\
        \resumeTitleListStart
            \resumeTitle{Application Engineer}{09/2023 - 01/2024}
                \resumeItemListStart
                    \resumeItem{Developed a palletizing software package for 4 and 6-axis Kawasaki Robots using the AS programming language and implemented it on-site at multiple customers.}
                    \resumeItem{Created robot programs for customer trade show booths that showcased the capabilities of their automation cells.}
                    \resumeItem{Conducted reach studies, speed tests, and cycle-time analysis in simulated and real-world environments.}
                    \resumeItem{Performed software and hardware testing of new robots and created test cells and specialized tooling needed for tests.}
                    \resumeItem{Consulted with systems integrators and end-users to develop robotic automation solutions, conducted on-site training on robot programming, and provided remote technical support concerning robot I/O and robot-PLC communication.}
                \resumeItemListEnd

            \resumeTitle{Field Service Engineer}{04/2023 - 09/2024}
                \resumeItemListStart
                    \resumeItem{Supported customers on-site and remotely by diagnosing and resolving mechanical, electrical, and software complications related to robot functionality.}
                    \resumeItem{Collaborated with the service team and engineering department to develop robotic automation solutions for systems integrators and end-users that improve customer retention and satisfaction.}
                \resumeItemListEnd
            \resumeTitleListEnd
            
            \bigskip
            
    \resumeSubHeading{Woco Tech USA}{Novi, Michigan}\\
        \resumeTitleListStart
            \resumeTitle{Design Engineer Intern}{06/2019 - 08/2021}
                \resumeItemListStart
                    \resumeItem{Created design proposals and updated existing designs to meet customers’ specifications.}
                    \resumeItem{Produced technical drawings and presentations for customers.}
                    \resumeItem{Reviewed and revised designs for tooling and manufacturing feasibility.}
                \resumeItemListEnd

            \resumeTitle{Engineering Intern}{05/2017 - 08/2017}
                \resumeItemListStart
                    \resumeItem{Ensured that automotive parts were made to specification through tolerance testing.}
                    \resumeItem{Responsible for quality review and inspection of both production and prototype parts while adhering to strict time constraints and standards.}
                \resumeItemListEnd
        \resumeTitleListEnd

  \resumeSubHeadingListEnd


% PROJECTS
\section{Projects}
    \resumeSubHeadingListStart
    
        \resumeSubHeading{\href{http://www.capstone.cse.msu.edu/2022-08/projects/union-pacific/}{Mobile Train Handling Simulator}}{\small{09/2022 - 12/2022}}\\
            \resumeItemListStart
                \resumeItem{Led a team of six students in Michigan State University’s computer science capstone course to design and build a mobile train handling simulator following the Agile methodology for the Union Pacific Railroad Company.}
                \resumeItem{Created for a Microsoft Surface Tablet and implemented with C\# using the Unity game engine, Microsoft's .NET framework on Windows, and a proprietary train-physics engine created by PS Technology.}
            \resumeItemListEnd
   \bigskip
        \resumeSubHeading{\href{https://github.com/Darien-Ford/Portfolio_Website}{Portfolio Website}}{\small08/2024 - Present}\\
            \resumeItemListStart
                \resumeItem{Created a portfolio/resume website using the React framework and Vite (HTML, CSS, JavaScript).}
                \resumeItem{Set up auto-deployment to Hostinger from a repository using GitHub actions.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd
  
 % EDUCATION
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubHeading{Michigan State University}{East Lansing, Michigan}\\
            \resumeTitleListStart
                \resumeTitle{Bachelor of Science, Computer Science; Minor in Business}{08/2017 - 12/2022}
            \resumeTitleListEnd
    \resumeSubHeadingListEnd
  
% SKILLS
\section{Skills}
    \resumeItemListStart
        \resumeItem{Python, C++, C, C\#, SQL, AS, Lua, Unity 2D, Git, GitHub}
        \resumeItem{Software Development, Data Structures and Algorithm Engineering, Object-Oriented Programming}
        \resumeItem{Robot Programming, Robot I/O, Robot-PLC Communication, Electrical Troubleshooting}
        \resumeItem{CATIA v5, NX, SolidWorks, AutoCAD, Inventor}
    \resumeItemListEnd

\end{document}

